\documentclass{tufte-handout}
\usepackage{amsmath, amsthm}

\title{Solutions to LADW by Sergei Treil}
\author{Kasyap Munukutla}
\date{}

\newtheorem{innercustomthm}{Prob.}
\newenvironment{prob}[1]
  {\renewcommand\theinnercustomthm{#1}\innercustomthm}
  {\endinnercustomthm}

\newcommand{\prob}[2]{\begin{prob}{#1}#2\end{prob}}\
\newcommand{\soln}{\begin{proof}#1\end{proof}}
    \newcommand{\vc}[2]{\textbf{#1}$_{#2}$}


\begin{document}
\maketitle
\prob{2.4.a}{Write down a basis for the space of 3 $\times$ 3 matrices.}
\proof{
    A matrix is symetric if it is equal to its transpose. For an 3 $\times$ 3 matrix $A$, this means that the following equivalences, where elements of $A$ are denoted $i,j$, must be true: 
        \begin{itemize}
            \item[] 1,2 = 2,1
            \item[] 3,1 = 1,3
            \item[] 3,2 = 2,3.
        \end{itemize}
    The main diagonal doesn't change with transposition. So we have the following basis that preserves the above equivalences as well as allowing for the main diagonal to be non zero. 
\begin{gather}
\alpha_{1}\begin{bmatrix}
1 & 0 & 0 \\
0 & 1 & 0 \\
0 & 0 & 1 
\end{bmatrix} + 
 \alpha_{2}\begin{bmatrix}
0 & 1 & 0 \\
1 & 0 & 0 \\
0 & 0 & 0 
\end{bmatrix}  
+
 \alpha_{3}\begin{bmatrix}
0 & 0 & 1 \\
0 & 0 & 0 \\
1 & 0 & 0 
\end{bmatrix}  
+
\alpha_{4}\begin{bmatrix}
0 & 0 & 0 \\
0 & 0 & 1 \\
0 & 1 & 0 
\end{bmatrix} 
\end{gather}
    }
\prob{2.5}{Is it possible that vectors \vc{v}{1}, \vc{v}{2}, and \vc{v}{3} are linearly dependent, but the vectors \vc{w}{1} = \vc{v}{1} + \vc{v}{2},
 \vc{w}{2} = \vc{v}{2} + \vc{v}{3}, \vc{w}{3} = \vc{v}{1} + \vc{v}{3} are linearly dependent?}
\proof{ This statement cannot be true. If the set of \vc{w}{} vectors is linearly independent, then the only solution to $\beta_{1}$\vc{w}{1} + $\beta_{2}$\vc{w}{2} + $\beta_{3}$\vc{w}{3} = $0$ would be trivial. But in expanding this out, $\beta_{1}$\vc{v}{1} + $\beta_{1}$\vcvw}{2} + $\beta_{2}$\vc{v}{2} + $\beta_{2}$\vc{v}{3} + $\beta_{3}$\vc{v}{3} + $\beta_{3}$\vc{v}{1} = $0$. 
    This further simplifies to: $\beta{1} + \beta{3}$\vc{v}{1} +  $\beta{1} + \beta{2}$\vc{v}{2}} +  $\beta{2} + \beta{3}$\vc{v}{3} = $0$. Thus if we can find a solution to the following set of equations, we have a linearly dependent set in \vc{w}{}. 
    $$ \beta_{1} + \beta_{3} &= \alpha_{1} \\
        \beta_{1} + \beta_{2} &= \alpha_{2} \\
        \beta_{2} + \beta_{3} &= \alpha_{3} $$
}
\end{document}
